---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# combinedevents

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/combinedevents)](https://CRAN.R-project.org/package=combinedevents)
[![Build Status](https://travis-ci.org/Katie-Frank/combinedevents.svg?branch=master)](https://travis-ci.org/Katie-Frank/combinedevents)
[![Codecov test coverage](https://codecov.io/gh/Katie-Frank/combinedevents/branch/master/graph/badge.svg)](https://codecov.io/gh/Katie-Frank/combinedevents?branch=master)
<!-- badges: end -->

## Overview

The **combinedevents** package provides functions to calculate scores and marks for track and field combined events competitions. The functions are based on the IAAF Scoring Tables for Combined Events. 

## Installation

You can install the released version of **combinedevents** from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("combinedevents")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Katie-Frank/combinedevents")
```

## Usage

The two main functions in the package are

- `scores()` calculates scores
- `marks()` calculates marks

Below are some quick examples. To learn more about **combinedevents**, see package documentation.

```{r example}
library(combinedevents)

# scores for men's decathlon

# marks for women's heptathlon
marks(c(900, 1014, 790, 1000, 788, 800, 1000), "female", "heptathlon")
```

