---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# combinedevents

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/combinedevents)](https://CRAN.R-project.org/package=combinedevents)
[![R build status](https://github.com/Katie-Frank/combinedevents/workflows/R-CMD-check/badge.svg)](https://github.com/Katie-Frank/combinedevents/actions)
[![codecov](https://codecov.io/gh/Katie-Frank/combinedevents/branch/master/graph/badge.svg)](https://codecov.io/gh/Katie-Frank/combinedevents)
[![Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/combinedevents)](https://cran.r-project.org/package=combinedevents)

<!-- badges: end -->

## Overview

**combinedevents** is an R package to calculate scores and marks for track and field combined events competitions. The functions included in this package are based on the scoring tables for combined events created by the International Association of Athletics Federation (2001).

## Installation

Version 0.1.1 will be on [CRAN](https://CRAN.R-project.org) soon (the package was submitted on 2/3). In the meantime, version 0.1.0 can be installed from CRAN with:

``` r
install.packages("combinedevents")
```

The development version of **combinedevents** can be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Katie-Frank/combinedevents")
```

## Usage

The two main functions in the package are

- `scores()` calculates scores
- `marks()` calculates marks

Below are a couple of quick examples. To learn more about **combinedevents**, see the package documentation.

```{r example}
library(combinedevents)

# scores for men's decathlon
scores(c(10.8, 7.1, 12, 2.05, 49.5, 14.5, 35, 4.6, 40, "4:21"), "male", "decathlon")

# marks for women's heptathlon
marks(c(900, 1014, 790, 1000, 788, 800, 1000), "female", "heptathlon")
```

## References

International Association of Athletics Federation (2001). *IAAF Scoring Tables for Combined Events*.
