---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# combinedevents

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/combinedevents)](https://CRAN.R-project.org/package=combinedevents)
[![R build status](https://github.com/Katie-Frank/combinedevents/workflows/R-CMD-check/badge.svg)](https://github.com/Katie-Frank/combinedevents/actions)
[![codecov](https://codecov.io/gh/Katie-Frank/combinedevents/branch/master/graph/badge.svg)](https://codecov.io/gh/Katie-Frank/combinedevents)

<!-- badges: end -->

## Overview

**combinedevents** is an R package to calculate scores and marks for track and field combined events competitions. The functions included in this package are based on the scoring tables for combined events set forth by the International Association of Athletics Federation (2001). These scoring tables are available for download as a PDF:

* Go to the [Technical Information Section of the World Athletics Website](https://www.worldathletics.org/about-iaaf/documents/technical-information)
* Select *Scoring Tables*
* Download *IAAF Scoring Tables for Combined Events*

## Installation

You can install the released version of **combinedevents** from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("combinedevents")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Katie-Frank/combinedevents")
```

## Usage

The two main functions in the package are

- `scores()` calculates scores
- `marks()` calculates marks

Below are two quick examples. To learn more about **combinedevents**, see the package documentation.

```{r example}
library(combinedevents)

# scores for men's decathlon
scores(c(10.8, 7.1, 12, 2.05, 49.5, 14.5, 35, 4.6, 40, "4:21"), "male", "decathlon")

# marks for women's heptathlon
marks(c(900, 1014, 790, 1000, 788, 800, 1000), "female", "heptathlon")
```

## References

International Association of Athletics Federation (2001). *IAAF Scoring Tables for Combined Events*.
